Increased productivity using Atomify - a real-time LAMMPS visualizer

### 2018-06-14 IOPLaTeX.tex
Fixed script and small stuwff

Any changes to the script like defining regions or groups,
changing temperatures, size of simulation box or inserting atoms can
quickly be verified since the visualization shows the real-time state of the simulator.
Rerunning the current script can be done by pressing \keys{Ctrl+R} (\keys{cmd+R} on macOS).

@@

\subsection{Creating the initial geometry}
We create a new script in Atomify using \keys{\ctrl+N}, and save it (\keys{\ctrl+S}) as \code{run.in}.
Copy the following input script

\todo[inline]{Should we remove line numbers?}
we will modify it part by part.
Here, we have a Lennard Jones solid with reduced density
$\rho^* = 0.975$, reduced masses $m_1^* = 4.0$, $m_2^* = 0.5$ with $(60\times30\times30)$
FCC unit cells and a cutoff of $2.5$. 
The force field parameters are chosen so that atoms of type 1
are in the solid phase while type 2 atoms are gas at reduced temperature $T^*=0.5$.
The two atom types are weakly coupled (small $\epsilon_{ij}$) so the gas atoms won't
stick too easily to the surface since this would prevent flow.

@@

The atoms inside the region can now be deleted with the following commands
\begin{lstlisting}
group cylinder1 region cylinder1
variable N_cyl equal count(cylinder1)
variable V equal PI*v_R*v_R*lx
variable rho_m equal 0.1
variable N_wanted equal $V*${rho_m}/0.5
variable delete_fraction equal (${N_cyl}-${N_wanted})/${N_cyl}
delete_atoms porosity cylinder1 ${delete_fraction} 1234
\end{lstlisting}
where we see the result in figure \ref{fig:initial_configuration}c by rerunning the script with \keys{\ctrl+R}.

This shows a powerful workflow with Atomify where changes quickly can be tested with immediate feedback.
Each time we add or change a command, we just rerun with \keys{\ctrl+R} to see how it looks like.

The next step now is to create a larger cylinder $C_2$, the one containing the orange atoms in
figure \ref{fig:cylinder_simulation}, where regular time integration will take place.
This cylinder should have a slightly bigger radius and can be created with another region command:
\begin{lstlisting}
region cylinder2 cylinder x $c $c $(v_R+6) EDGE EDGE units box
\end{lstlisting}
Again press \keys{\ctrl+R} to see the expected result in figure \ref{fig:initial_configuration}d.

@@

By rerunning again (\keys{\ctrl+R}), we confirm that the system behaves as expected as shown in figure \ref{fig:moving_atoms} where
atoms are colored based on their displacement.
The only remaining part now is to set up the commands that will apply the pressure gradient and measure the radial velocity profile.

@@

\section{\label{sec:discussion}Discussion}
In this paper we have presented Atomify, an new software that reduces the amount of context switches and mouse clicks
when developing new simulation scripts.
As of today, only LAMMPS is supported as the physical simulator, but other codes can easily be integrated
due our general implementation with no assumpetion about the underlying code except atom positions.
The communication overhead is minimized since LAMMPS runs in the same process as Atomify, sharing the memory.

@@

\todo[inline]{Potentially future work, emscripten, webassembly? emscripten has a proceedings paper.}

>>>>

Any changes to the script like defining regions or groups,
changing temperatures, size of simulation box or inserting atoms can
quickly be verified since the visualization shows the real-time state of the simulator.
Rerunning the current script can be done by pressing \keys{Ctrl+R} (\keys{\cmd+R} on macOS).

@@

\subsection{Creating the initial geometry}
We create a new script in Atomify using \keys{Ctrl+N}, and save it with \keys{Ctrl+S} as \code{run.in}.
Copy the following input script

\lstinputlisting[language=LAMMPS]{simple.in}

We will modify this script bit by bit.
Here, we have a Lennard Jones solid with reduced density
$\rho^* = 0.975$, reduced masses $m_1^* = 4.0$, $m_2^* = 0.5$ with $(60\times30\times30)$
FCC unit cells and a cutoff of $2.5$. 
The force field parameters are chosen so that atoms of type 1
are in the solid phase while type 2 atoms are gas at reduced temperature $T^*=0.5$.
The two atom types are weakly coupled (small $\epsilon_{ij}$) so the gas atoms won't
stick too easily to the surface since this would prevent flow.

@@

The atoms inside the region can now be deleted with the following commands
\begin{lstlisting}
group cylinder1 region cylinder1
variable N_cyl equal count(cylinder1)
variable V equal PI*v_R*v_R*lx
variable rho_m equal 0.1
variable N_wanted equal $V*${rho_m}/0.5
variable delete_fraction equal (${N_cyl}-${N_wanted})/${N_cyl}
delete_atoms porosity cylinder1 ${delete_fraction} 1234
\end{lstlisting}
where we see the result in figure \ref{fig:initial_configuration}c by rerunning the script with \keys{Ctrl+R}.

This shows a powerful workflow with Atomify where changes quickly can be tested with immediate feedback.
Each time we add or change a command, we just rerun with \keys{Ctrl+R} to see how it looks like.

The next step now is to create a larger cylinder $C_2$, the one containing the orange atoms in
figure \ref{fig:cylinder_simulation}, where regular time integration will take place.
This cylinder should have a slightly bigger radius and can be created with another region command:
\begin{lstlisting}
region cylinder2 cylinder x $c $c $(v_R+6) EDGE EDGE units box
\end{lstlisting}
Again press \keys{Ctrl+R} to see the expected result in figure \ref{fig:initial_configuration}d.

@@

By rerunning again (\keys{Ctrl+R}), we confirm that the system behaves as expected as shown in figure \ref{fig:moving_atoms} where
atoms are colored based on their displacement.
The only remaining part now is to set up the commands that will apply the pressure gradient and measure the radial velocity profile.

@@

@@
